On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-05-21 Manuscript/manuscript.tex
BC and question about BCA

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI is described in 
\citet{efron1993introduction}.
A $(1 - \alpha$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{SE}, \hat{\theta}_{n} -
t_{(\alpha/2), k -1}\hat{SE}),
\]
where $k$ is the number of blocks.
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Like the standard 
normal interval, the Student's $t$ CI is a table-based bootstrap interval
approach. In this case,
its validity relies on whether the distribution of $\hat\theta_n$ is
reasonably well approximation by the $t_{k-1}$ distribution with an
expected value of $\theta$, and whether the bootstrap 
$\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Percentile CI}
The percentile interval was first suggested in \citet{efron1979bootstrap}.
Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)$
empirical percentile CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)}, \hat\theta_{n, 1 - \alpha/2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.
As will be shown in our simulation study, this approach works well for the
marginal mean and standard deviation of a serially dependent process, but its
coverage of the temporal dependence deteriorates as $n$ increases, which is
contrary to what one would expect.

@@

When using Student's $t$ centered intervals and $\phi$ is
unknown, the results of this study suggest that an $n$ of around $3200$ may be
necessary for common practice to estimate simpler parameters like $\mu$ 
or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
to
estimate these parameters. For lower absolute values of $\phi$, a smaller
$n$ is sufficient when estimating $\mu$ or $\sigma$. For negative
values of $\phi$, coverage of $\mu$ is higher in general. In fact, 
Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$, 
meaning that if $\phi$ is known to have a very negative value, another CI
should be used.
$However, in real world applications, $\phi$ is
more commonly found to be positive, so Student's $t$ should still be used
if $\phi$ is unknown.
Lastly, to estimate $\phi$, an $n$ of around $800$ using the 
Student's $t$ method
 may be sufficient.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.

>>>>

\paragraph{Student's $t$ CI}
The procedure for constructing a Student's $t$ CI based on standard bootstrap is
described in \citet{efron1993introduction}. \jy{give page or section number when
  citing a book}
With block bootstrapping, a $(1 - \alpha)$ Student's $t$ CI is
\[
(\hat{\theta}_{n} - t_{(1-\alpha/2), k - 1}\hat{\text{SE}}, \quad
\hat{\theta}_{n} - t_{(\alpha/2), k -1}\hat{\text{SE}}),
\]
where $k$ is the number of blocks.
This CI is centered by the point estimator $\hat\theta_n$ and is symmetric.
Like the standard 
normal interval, the Student's $t$ CI is a table-based bootstrap interval
approach. In this case,
its validity relies on whether the distribution of $\hat\theta_n$ is
reasonably well approximation by the $t_{k-1}$ distribution with an
expected value of $\theta$, and whether the bootstrap 
$\widehat{\text{SE}}$ approximates the true standard error.

\paragraph{Percentile CI}
The percentile CI was first suggested in \citet{efron1979bootstrap}.
Let $\hat\theta_{n, \alpha}^{(b)}$ be the empirical $100\alpha$th percentile of
$\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$. The $(1 - \alpha)$
empirical percentile CI is
\[
(\hat\theta_{n, \alpha/2}^{(b)}, \quad \hat\theta_{n, 1 - \alpha/2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$.
As will be shown in our simulation study, this approach works well for the
marginal mean and standard deviation of a serially dependent process, but its
coverage of the temporal dependence deteriorates as $n$ increases, which is
contrary to what one would expect.

@@

When using Student's $t$ centered intervals and $\phi$ is
unknown, the results of this study suggest that an $n$ of around $3200$ may be
necessary for common practice to estimate simpler parameters like $\mu$ 
or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
to
estimate these parameters. For lower absolute values of $\phi$, a smaller
$n$ is sufficient when estimating $\mu$ or $\sigma$. For negative
values of $\phi$, coverage of $\mu$ is higher in general. In fact, 
Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$, 
meaning that if $\phi$ is known to have a very negative value, another CI
should be used.
However, in real world applications, $\phi$ is
more commonly found to be positive, so Student's $t$ should still be used
if $\phi$ is unknown.
Lastly, to estimate $\phi$, an $n$ of around $800$ using the 
Student's $t$ method
 may be sufficient.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.
